---
title: "P8105_hw5_sy2825"
author: "Shuo Yan (sy2825)"
output: github_document
date: "2018-11-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)


```

# Poblem 1

First, let's import data and create a tidy dataframe containing data from all participants.

```{r import_and_tidy_longitudinal_data}

file_names = list.files(path = "./data", pattern = ".*csv")

file_data = map(file_names, ~ read.csv(file.path("./data", .)))

longitudinal_data = tibble(name = str_replace(file_names, ".csv", "")) %>%
  mutate(file_data = file_data) %>%
  unnest() %>%
  janitor::clean_names() %>%
  gather(key = week, value = observations, week_1:week_8) %>%
  mutate(week = str_replace(week, "week_", "")) %>%
  separate(name, into = c("arm", "id"), sep = "_") %>%
  mutate(arm = str_replace(arm, "con", "control")) %>%
  mutate(arm = str_replace(arm, "exp", "experimental"))

# Now we have a tidied dataframe :

longitudinal_data
```

The following is the spaghetti plot showing observations on each subject over time :

```{r longitudinal_data_plot}

ggplot(longitudinal_data, aes(x = week, y = observations, group = id, color = id)) +
  geom_path() + 
  labs(title = "Observations on each subject over time",
       x = "Week",
       y = "Observations") + 
  viridis::scale_color_viridis(
    name = "Subject ID", 
    discrete = TRUE) +
  facet_grid(. ~ arm) +
  theme(plot.title = element_text(hjust = 0.5))
```

From the plot we can see that the observation values of experimental group are mostly higher than the observation values of control group. Also, the observation values of experimental group tend to increase over time.


# Problem 2

First, let's import and describe the raw data.

```{r describe_raw_washington_post_data}

url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

washington_post_data = read.csv(url)

setNames(
data.frame(colnames(washington_post_data)),
c("variable name")
)

```

The raw data is a data with dimension `r dim(washington_post_data)`. It includes 12 distinct variales that can describe the information about case id, case reported date, case location (city, state, latitude, and lontitude), disposition, and also victim's name (last name and first name), race , age, and sex.

Now let's tidy the data.

```{r tidy_washington_post_data}

tidy_washington_post_data = washington_post_data %>%
  janitor::clean_names() %>%
  mutate(city_state = paste(washington_post_data$city, washington_post_data$state, sep = ", ")) %>%
  group_by(city_state) %>%
  summarize(total_homicides = n(), total_unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))

tidy_washington_post_data
```
The above table shows the total number of homicides and the number of unsolved homicides for each city.

Now let's estimate the proportion of homicides that are unsolved for the city of Baltimore, MD.

```{r proportion_unsolved_baltimore_md}

baltimore_md = tidy_washington_post_data %>%
  filter(city_state == "Baltimore, MD")

baltimore_md_prop_test = prop.test(baltimore_md$total_unsolved_homicides, 
                                   baltimore_md$total_homicides)

broom::tidy(baltimore_md_prop_test) %>%
  select(1, 5, 6)
```

From the test we can know that the estimated proportion of homicides that are unsolved for the city of Baltimore, MD is 64.6% and the confidence intervale is from 62.8% to 66.3%.
